---
title: "Assignment2 607"
author: "Maliat"
date: "2/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

### For this assignment six recent movies have been chosen and rated. the ratings have been stored in sql workbench and transferred into R studio.



```{r include=FALSE}
setwd("C:/Users/malia/OneDrive/Desktop/MSDS DATA 607")
library(kableExtra)
library(RMySQL)
library(RODBC)
library(dplyr)
library(zoo)



install.packages("imputeTS",repos = "http://cran.us.r-project.org")
install.packages("reshape2",repos = "http://cran.us.r-project.org")

```

```{r}
defaultW <- getOption("warning") 

options(warning = -1) 

options(warning = defaultW)
```


### Hiding Database Password

```{r include=FALSE}
psswd <- .rs.askForPassword("")
con <- dbConnect(MySQL(), user="root", password=psswd, 
             dbname="assignment_2_607", host="localhost",
             client.flag=CLIENT_MULTI_STATEMENTS)

```



```{r}
SQLMovieData <- dbGetQuery(conn, "SELECT * FROM assignment_2_607.`movie rating 2`;")
SQLMovieData
```

```{r}

SQLMovieData$"Movie 1 Promising Young woman"[is.na(SQLMovieData$"Movie 1 Promising Young woman")]<-mean(SQLMovieData$"Movie 1 Promising Young woman",na.rm = TRUE)
```


```{r}
SQLMovieData
```

### Missing values have been replaced using mean values from the rating.

```{r}
library(imputeTS)
SQLMovieData1<-na_mean(SQLMovieData)

```

```{r}
library(reshape2)
ArrangedData <-melt(SQLMovieData1, id.vars = c("Name"))
names(ArrangedData)[2:3]<- c("Movie", "Rating")
ArrangedData$Rating<-as.numeric(ArrangedData$Rating)
ArrangedData
```


```{r}
library(ggplot2)
ggplot(data=ArrangedData, aes(x=Rating, y = Movie, fill = Rating, label = Rating))+
    geom_bar(stat="identity")+ 
    facet_wrap(~Name)+
    ggtitle("Movie Ratings by Family and Friends")+
    theme(axis.text.x = element_blank(),plot.title = element_text(hjust=0.5),legend.position = "right")
```


### Standardization will not work here because the ratings belong to same range of numbers. However, if they had different range of numbers, standardization would have been necessary.
